\documentclass[10pt]{article}
\usepackage{resume} 

\pagestyle{empty}

\begin{document}

\headerline{John Doe}{Data Scientist Example Resume} 

\begin{contactblock}[3]
  \contactline{\faPhone}{(999) 999-9999}
  \contactline{\faEnvelope}{\href{mailto:john.doe@example.com}{john.doe@example.com}}
  \contactline{\faLinkedin}{\href{https:x//www.linkedin.com/in/johndoe}{linkedin.com/in/johndoe}}
  \contactline{\faGithub}{\href{https:x//github.com/johndoe}{github.com/johndoe}}
  \contactline{\faMapMarker*}{Springfield, USA}
\end{contactblock}

\smallskip

Data scientist with a passion for turning raw data into actionable insights. Experienced in analytics, engineering, and visualization with a strong foundation in statistical modeling and machine learning.

% ----- Skills -----
\section*{Skills}
\begin{skillsblock}
  \skill{Programming}{\textbf{Python, SQL, PySpark}, R, MATLAB, Java}
  \skill{Architecture}{\textbf{Databricks, Snowflake}, AWS, Azure, Docker, APIs}
  \skill{Analytics}{\textbf{Machine Learning, Predictive Modeling}, Causal Inference, Time-Series Forecasting}
  \skill{Visualization}{\textbf{Tableau, Plotly, Excel}, Power BI, Data Storytelling}
  \skill{Collaboration}{\textbf{Git, JIRA}, Agile, Cross-Functional Team Leadership}
\end{skillsblock}

% ----- Experience -----
\section*{Professional Experience}

\experience{Senior Data Scientist}{Fictional Analytics Inc., Remote}{2022 -- Now}{
As a senior member of the data team, I focus on designing end-to-end solutions for predictive modeling and analytics that directly impact strategic decision-making. I work across engineering, analytics, and business units to ensure scalable, reliable, and interpretable data products.
\begin{itemize}
  \item Developed predictive models for customer retention, increasing accuracy by 20\%.
  \item Built scalable ETL pipelines for integrating data across multiple cloud platforms.
  \item Led a cross-functional team to deploy real-time dashboards for executive reporting.
\end{itemize}
}

\experience{Data Analyst}{Example Corp, New York, NY}{2019 -- 2022}{
Supported business operations by designing and maintaining analytic solutions for marketing, sales, and finance. Collaborated with stakeholders to translate business needs into actionable insights, while ensuring data quality and consistency across platforms.
\begin{itemize}
  \item Automated reporting workflows, reducing manual effort by 40\%.
  \item Conducted exploratory data analysis to uncover cost-saving opportunities.
  \item Designed and delivered visualizations that improved decision-making across teams.
\end{itemize}
}

\experience{Research Assistant}{University Data Lab, Springfield, USA}{2017 -- 2019}{
Worked within an academic research lab applying machine learning and statistical methods to real-world datasets. Supported faculty-led grants and mentored undergraduate students on applied data science projects.
\begin{itemize}
  \item Supported faculty projects with statistical modeling and survey data analysis.
  \item Co-authored two conference presentations on applied machine learning in healthcare.
\end{itemize}
}

% ----- Education -----
\section*{Education \& Credentials}

\experience{M.S. in Data Science}{Springfield University}{2017 -- 2019}{%
Thesis: Predictive Modeling of Renewable Energy Consumption Using Machine Learning.
}

\experience{B.S. in Computer Science}{State College}{2013 -- 2017}{%
Minor in Mathematics; graduated magna cum laude.
}

\experience{Certification}{Professional Data Scientist (PDS)}{2021}{%
Industry-recognized certification in applied data science and analytics.
}

\end{document}
